---
title: "Report Template"
author: "Lingyan Yu"
date: "`r Sys.Date()`"
status: "Published"
version: "1.0"
format:
    html:
        code-fold: true
---

```{r setup, include=FALSE}
if (!requireNamespace("pacman", quietly = TRUE)) {
    install.packages("pacman")
}
pacman::p_load(here, tidyverse)
```

```{r Load data and source functions}

```

## (TO DELETE) Template Notes

### 1) Naming Conventions

-   Section: Title Case
-   Code Chunk: Sentence Case

### 2) Ordered Section Headings

``` markdown
## 1.
### 1) 
#### I. 
**i)**
```

### 3) Subsection Code Chunks

-   Benefits: error tracking, caching\
-   Figure referencing: Each figure with their own chunks\
    **Figures generated by code chunks are automatically named based on the
    chunk name**

### 4) RERUN Messages

-   (NO NEED TO RERUN)\
-   (DO NOT RERUN UNLESS INTENDING TO UPDATE)

### 5) Tags

-   *Questionable*
-   TODO:

## 1. Import Data

```{r}

```

## 2. Data Preprocessing

```{r}

```

## 3. Data Transformation

```{r}

```

## 4. Data Subsetting

```{r}

```

## Start running here if no dataset updates.

## 5. Data Analyses

```{r}

```

## 6. Data Visualization

```{r}

```

## Session information

```{r}
sessionInfo()
```
