---
title: "Report Template"
author: "Lingyan Yu"
date: "`r Sys.Date()`"
toc: true
status: "Published"
version: "2.0"
format:
    html:
        html-math-method: katex
        code-tools: true
        self-contained: true
execute: 
    warning: false
---

```{r Load libraries}
if (!requireNamespace("pacman", quietly = TRUE)) {
    install.packages("pacman")
}
pacman::p_load(here, tidyverse, plotly)
```

```{r Load data and source functions}

```

## (TO DELETE) Template Notes

### 1) Naming Conventions

-   Section: Title Case
-   Code Chunk: Sentence Case

### 2) Ordered Section Headings

``` markdown
## 1.
### 1) 
#### I. 
**i)**
```

### 3) Subsection Code Chunks

-   Benefits: error tracking, caching\
-   Figure referencing: Each figure with their own chunks\
    **Figures generated by code chunks are automatically named based on the
    chunk name**

### 4) RERUN Messages

-   (NO NEED TO RERUN)     
-   (DO NOT RERUN UNLESS INTENDING TO UPDATE)

### 5) Tags

-   *Questionable*
-   TODO:

## 1. Import Data

```{r}

```

## 2. Data Preprocessing

```{r}

```

## 3. Data Transformation

```{r}

```

## 4. Data Subsetting

```{r}

```

### Tables

Use the `knitr::kable()` function to print tables as HTML:
```{r}
knitr::kable(head(ggplot2::diamonds))
```

## 5. Data Analyses

### LaTeX Math

$$
P\left(A=2\middle|\frac{A^2}{B}>4\right)
$$

## 6. Data Visualization

### Static Plot
```{r}
#| label: fig-dat
#| fig-cap: "Dat"
#| code-fold: true
dat <- data.frame(cond = rep(c("A", "B"), each=10),
                  xvar = 1:20 + rnorm(20,sd=3),
                  yvar = 1:20 + rnorm(20,sd=3))

ggplot(dat, aes(x=xvar, y=yvar)) +
    geom_point(shape=1) + 
    geom_smooth() 
```
Note that the `code-fold: true` parameter was added to the code chunk to hide the code by default.  
The use of the `label` and `fig-cap` options make this a cross-referenceable figure (see @fig-dat).    

### Interactive Plot
```{r}
#| label: fig-temperatures
#| fig-cap: "New Haven Temperatures"

pacman:p_load(dygraphs)
dygraph(nhtemp) %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```

## Session information

```{r}
sessionInfo()
```

## Acknowledgements

Quarto Gallery
- [Quarto HTML Basics](https://quarto-dev.github.io/quarto-gallery/articles/html/html.html)
- [A Quarto Page Layout Example](https://quarto-dev.github.io/quarto-gallery/page-layout/tufte.html)
  