---
title: "R Environment Management"
author: "Lingyan Yu"
date: "`r Sys.Date()`"
status: "Published"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
  markdown:
    wrap: 80
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. R Environment Management In an R Project

Initiate R environment management by creating a `renv.lock` snapshot and a
project-specific library:

```{r}
renv::init()
```

To update the library is to take a new snapshot: `renv::snapshot()`

# 2. If There Exists Subprojects

Create a `.Rprofile` file in the subproject folder and write `renv::autoload()`
into the file.

Opening the subproject session will automatically load the environment
configured and maintained in the upper level.

# 3. Sync the Environment Across Machines

Git only needs to track the `renv.lock` in R projects.

-   One may restore the environment by running `renv::restore()` in the R console
    with the environment snapshot stored in `renv.lock`.
-   Actual `renv` library folder is typically too large for GitHub.
-   Optional: tracking the `renv` library folder as well to save installation
    time based on the `renv.lock` snapshot

The restoring process can be automated by adding the following code to the R
script:

``` r
if (!requireNamespace("renv", quietly = TRUE)) install.packages("renv")
renv::restore()
```

However, the restoring process can be time-consuming and may require some manual
resolutions.

One may want to run the script in the background or backup the `renv` folder
using cloud storage when switching to a new machine for the first time.
