---
title: "Report Template"
author: "Lingyan Yu"
date: "`r Sys.Date()`"
status: "Published"
output: 
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
  markdown:
    wrap: 80
---

```{r setup, include=FALSE}
# Install and load the pacman package if not already loaded
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}
library(pacman)

pacman::p_load(here, tidyverse, conflicted)
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::filter)
# !diagnostics level=core
knitr::opts_chunk$set(echo = TRUE, fig.show = "asis")
```

```{r Load data and source functions}

```

# (TO DELETE) Template Notes
## 1) Naming Conventions
- Section: Title Case
- Code Chunk: Sentence Case

## 2) Ordered Section Headings
## 1)
### i.
#### A.
##### a) 

## 3) Subsection Code Chunks
- Benefits: error tracking, caching     
- Figure referencing: Each figure with their own chunks     
**Figures generated by code chunks are automatically named based on the chunk name**

## 4) RERUN Messages
- (NO NEED TO RERUN)  
- (DO NOT RERUN UNLESS INTENDING TO UPDATE)  

## 5) Tags
- *Questionable*
- TODO:

# 1. Import Data
```{r}

```

# 2. Data Preprocessing
```{r}

```

# 3. Data Transformation
```{r}

```

# 4. Data Subsetting
```{r}

```

# Start running here if no dataset updates.

# 5. Data Analyses
```{r}

```

# 6. Data Visualization
```{r}

```

# Session information
```{r}
sessionInfo()
```